The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-03-07 paper/ms.tex
Updated Table 1 with lots more measurements
Added new detections to table.
Removed low vsini primaries from sample and detections tables.
Updated search methodology for hot grid.

TODO: MAKE THE SPECTRA AVAILABLE SOMEHOW...

@@

@@

In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference measurements in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. We also derive the projected separation in AU and the companion mass from the images. We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{Hipparchos}. We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}). For each sample, we use a grid of Kurucz stellar model spectra [CITE] and the pysynphot code [CITE] to determine the companion temperature needed to replicate the observed magnitude difference. We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample. We convert the best temperature to a companion mass using the same isochrone grid. The masses derived from the imaging data have very large uncertainties because the primary star property estimates that they depend on are very uncertain.

@@

For the optical data, we use the blue echelle orders ($\lambda < 5550 \AA$). We ignore the strong hydrogren Balmer lines in the spectrum because they span several echelle orders and make continuum normalization very difficult, potentially biasing the result. There are sufficient metal lines in the optical spectra that the resulting CCF always has a very strong peak at the radial velocity of the primary star. The near-infrared IGRINS spectra have very few strong metal lines; we use the subset from $1.51 - 1.73 \micron$ that is dominated by hydrogren Brackett lines for these spectra. We then estimate the temperature and surface gravity of the primary stars from the CCF with the largest peak. We adopt the following errors on the temperature and surface gravity:

\begin{align}
 \sigma_T &= \begin{cases}
      \hfill 300\ K \hfill & T < 10000\ K \\
      \hfill 1000\ K \hfill & T >= 10000\ K \\
     \end{cases} \\
 \sigma_{\log{g}} &= 0.25
\end{align}

Next, we use Padova stellar evolutionary tracks \citep{Bressan2012} and the isochrones code \citep{isochrones_code} to estimate the mass and age of the system from the measured temperature and $\log{g}$. As a consistency check, we also interpolate from a table of stellar properties as a function of spectral type \citep{Pecaut2013} to estimate the primary mass from the published spectral types. We show the comparison in Figure \ref{fig:prim_mass}. We estimate uncertainties in the spectral type mass by assuming a spectral type uncertainty of $\pm 0.5$ spectral types and propagating to mass. There is excellent agreement between the masses we measure and the spectral type masses.

@@

We show the temperature, surface gravity, mass, and age estimates for all primary stars in Table \ref{tab:sample}. The MCMC samples generated by the isochrones code are available at [GIVE ZENODO LINK OR SOMETHING].

@@

To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection/recovery experiments. We started by creating synthetic binary star observations from each of our observed spectra. We made two distinct grids of companion stars: a low temperature grid spanning

@@

Next, we cross correlated all of the synthetic observations against the Phoenix model template that was used to construct them. We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity. We then combined all of the radial velocity trials for each grid point to estimate a probability of detection at that grid point:

@@

@@

     HIP 813 &           B9Vn &    00:10:02.20 &   +11:08:44.93 &   5.537 &     10.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &   5.757 &      9.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 1366 &            A2V &    00:17:05.50 &   +38:40:53.89 &   4.610 &     10.56 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &   5.498 &     10.25 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &   5.190 &     18.83 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &   4.732 &      8.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $78^{+70}_{-52}$ &      1 \\
    HIP 2912 &            B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3300 &            B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3741 &            B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &   5.532 &     11.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $307^{+234}_{-196}$ &      1 \\
    HIP 5348 &            B6V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &   5.318 &     11.78 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &   5.600 &     12.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &   5.619 &     16.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &   5.177 &     11.75 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &   5.520 &      2.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
      HR 545 &          B9.5V &    01:53:31.77 &   +19:17:46.27 &   4.700 &   \nodata &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  2 \\
    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &   5.283 &     13.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 9564 &           A1Vn &    02:02:52.48 &   +64:54:05.27 &   5.999 &     11.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
      HR 604 &            B8V &    02:03:54.72 &   +42:19:51.41 &   5.820 &   \nodata &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  2 \\
   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &   5.261 &     10.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &   4.000 &     29.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 10732 &           A1Vn &    02:18:07.54 &   +19:54:04.19 &   5.575 &      7.29 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  2 \\
   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &   4.869 &      7.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &   5.454 &      9.68 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  2 \\
   HIP 12706 &           A2Vn &    02:43:18.04 &   +03:14:08.94 &   3.470 &     40.97 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+105}_{-188}$ &      1 \\
   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &   4.670 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &   5.776 &      5.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &   5.314 &      4.18 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  2 \\
   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &   5.389 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &   3.606 &     19.69 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &   5.514 &      6.60 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  2 \\
   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &   5.160 &     17.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &   4.700 &     10.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14043 &            B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14293 &            A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.28}_{-0.23}$ &    $139^{+16}_{-25}$ &      1 \\
   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  2 \\
   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &   4.840 &     19.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &   4.880 &     12.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &   5.478 &      4.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &   5.158 &      5.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15444 &            B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16147 &            B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\

@@

   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &   4.678 &      6.05 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  2 \\
   HIP 16285 &            A5V &    03:29:55.15 &   -42:38:03.32 &   5.768 &     15.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &   5.125 &      9.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\

>>>>

All of the reduced and telluric-corrected spectra used in this study will be released with this work, and will be available at the following url: \url{https://zenodo.org/record/46482}.

@@

In order to be sensitive to hot companions, we additionally cross-correlate the spectra against a second grid of Kurucz model spectra \citep{Castelli2003}. The change in model is necessary because the Phoenix model library does not extend beyond $12000\ K$. The Kurucz grid is defined as follows:

\begin{itemize}
\item $T_\mathrm{eff} = 9000-30000$ K, in steps of 1000 K
\item {[}Fe/H{]} = -0.5, 0.0, +0.5
\item $v\sin{i} = 1, 5, 10, 20, 30, 40, 50 \ \mathrm{km\ s}^{-1}$
\end{itemize}

@@

In addition we obtained Gemini/NIRI adaptive optics imaging data for 18 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference measurements in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. We also derive the projected separation in AU and the companion mass from the images. We calculate the separation from the measured angular separation and the Hipparchos parallax \citep{Hipparchos}. We calculate the companion mass and uncertainties from 1000 samples of the magnitude difference measurement and the primary star mass, temperature, age, and radius (see Section \ref{sec:sp}). For each sample, we use a grid of Kurucz stellar model spectra \citep{Castelli2003}and the pysynphot code\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} to determine the companion temperature needed to replicate the observed magnitude difference. We estimate the companion radius by interpolating solar metallicity Dartmouth isochrones [CITE] from the companion temperature and system age sample. We convert the best temperature to a companion mass using the same isochrone grid. The masses derived from the imaging data have very large uncertainties because the primary star property estimates that they depend on are very uncertain.

@@

For the optical data, we use the blue \'echelle orders ($\lambda < 5550 \AA$). We ignore the strong hydrogren Balmer lines in the spectrum because they span several \'echelle orders and make continuum normalization very difficult, potentially biasing the result. There are sufficient metal lines in the optical spectra that the resulting CCF always has a very strong peak at the radial velocity of the primary star. The near-infrared IGRINS spectra have very few strong metal lines; we use the subset from $1.51 - 1.73 \micron$ that is dominated by hydrogren Brackett lines for these spectra.  We then estimate the temperature and surface gravity of the primary stars from the CCF with the largest peak. We adopt the following errors on the temperature and surface gravity:

\begin{align}
 \sigma_T &= \begin{cases}
      \hfill 500\ K \hfill & T < 10000\ K \\
      \hfill 1000\ K \hfill & T >= 10000\ K \\
     \end{cases} \\
 \sigma_{\log{g}} &= 0.25
\end{align}
The IGRINS parameters are less reliable because they rely almost solely on the hydrogren Brackett lines that span an entire \'echelle order, so we double the uncertainty on the IGRINS-derived temperature, surface gravity, and metallicity. Additionally, we throw out the IGRINS parameters if the star was also observed by one of the optical instruments in our survey. For stars observed multiple times, we use the average parameters and reduce the uncertainties accordingly.

Next, we use Padova stellar evolutionary tracks \citep{Bressan2012} and the isochrones code \citep{isochrones_code} to estimate the mass and age of the system from the measured temperature and surface gravity. As a consistency check, we also interpolate from a table of stellar properties as a function of spectral type \citep{Pecaut2013} to estimate the primary mass from the published spectral types. We show the comparison in Figure \ref{fig:prim_mass}. We estimate uncertainties in the spectral type mass by assuming a spectral type uncertainty of $\pm 0.5$ spectral types and propagating to mass. There is excellent agreement between the masses we measure and the spectral type masses.

@@

We show the temperature, surface gravity, mass, and age estimates for most of our sample stars Table \ref{tab:sample}. We do not give parameters for the few stars that show strong discrepancies with the spectral-type estimate, most of which are early B-stars that have temperatures higher than the maximum grid temperature of $30000\ K$. The MCMC samples generated by the isochrones code are available at the following url: \url{https://zenodo.org/record/46482}.

@@

To quantify the detection rate as a function of companion temperature and $v\sin{i}$, we performed a series of injection and recovery experiments. We started by creating synthetic binary star observations from each of our observed spectra. We made two distinct grids of companion stars: a low temperature grid spanning

@@

Next, we cross correlated all of the synthetic observations against the Phoenix model template that was used to construct them. We counted the companion as detected if the highest point in the resulting CCF was found at the correct radial velocity, and if the peak had a significance of $>5\sigma$, where $\sigma$ is the standard deviation of the CCF for points more than $100\ \mathrm{km\ s}^{-1}$ away from the peak. We then combined all of the radial velocity trials for each grid point to estimate a probability of detection at that grid point:

@@

TODO: Discuss fudge factor if Adam agrees...

@@

     HIP 813 &     B9Vn &    00:10:02.20 &   +11:08:44.93 &   5.537 &     10.68 &   $12516 \pm 426$ &  $4.3 \pm 0.14$ &  $3.1^{+0.18}_{-0.17}$ &      $85^{+56}_{-52}$ &       1 \\
    HIP 1191 &    B8.5V &    00:14:54.52 &   -09:34:10.45 &   5.757 &      9.63 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.41}_{-0.37}$ &      $23^{+63}_{-16}$ &       2 \\
    HIP 1366 &      A2V &    00:17:05.50 &   +38:40:53.89 &   4.610 &     10.56 &    $9371 \pm 319$ &  $4.0 \pm 0.14$ &  $2.2^{+0.18}_{-0.16}$ &    $464^{+83}_{-119}$ &       1 \\
    HIP 1647 &      B9V &    00:20:39.04 &   -69:37:29.68 &   5.498 &     10.25 &   $11393 \pm 387$ &  $4.0 \pm 0.14$ &  $2.8^{+0.21}_{-0.18}$ &     $206^{+48}_{-79}$ &       1 \\
    HIP 2381 &      A3V &    00:30:22.65 &   -23:47:15.65 &   5.190 &     18.83 &    $8364 \pm 284$ &  $4.0 \pm 0.14$ &  $1.9^{+0.16}_{-0.13}$ &   $715^{+135}_{-183}$ &       1 \\
    HIP 2505 &     B8Vn &    00:31:46.36 &   +54:31:20.23 &   4.732 &      8.64 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.45}_{-0.40}$ &     $58^{+104}_{-48}$ &       2 \\
    HIP 2548 &    B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &      $77^{+69}_{-51}$ &       1 \\
    HIP 2912 &      B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &  $16000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.7^{+0.61}_{-0.54}$ &      $26^{+32}_{-18}$ &       2 \\
    HIP 3300 &      B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &  $18000 \pm 1000$ &  $4.0 \pm 0.25$ &  $5.7^{+0.67}_{-0.63}$ &      $19^{+19}_{-13}$ &       2 \\
    HIP 3478 &      B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.60}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
    HIP 3741 &      B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.47}_{-0.42}$ &    $282^{+82}_{-115}$ &       2 \\
    HIP 3881 &      B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &  $16000 \pm 1000$ &  $4.2 \pm 0.25$ &  $4.5^{+0.58}_{-0.52}$ &      $17^{+28}_{-11}$ &       2 \\
    HIP 4436 &      A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &    $8351 \pm 284$ &  $4.0 \pm 0.14$ &  $1.9^{+0.17}_{-0.14}$ &   $733^{+129}_{-158}$ &       1 \\
    HIP 5131 &     A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &   $11956 \pm 406$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.14}$ &      $69^{+65}_{-45}$ &       1 \\
    HIP 5132 &     A0Vn &    01:05:41.71 &   +21:27:55.60 &   5.532 &     11.64 &   $12053 \pm 410$ &  $4.4 \pm 0.14$ &  $2.9^{+0.16}_{-0.14}$ &      $64^{+61}_{-42}$ &       1 \\
    HIP 5310 &      A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &   $307^{+228}_{-196}$ &       1 \\
    HIP 5348 &  B6V+B9V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &   $13776 \pm 468$ &  $4.2 \pm 0.14$ &  $3.6^{+0.23}_{-0.21}$ &      $67^{+38}_{-39}$ &       1 \\
    HIP 5361 &      B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.49}_{-0.43}$ &      $18^{+36}_{-11}$ &       2 \\
    HIP 5518 &    A0Vnn &    01:10:39.32 &   +68:46:43.04 &   5.318 &     11.78 &   $11894 \pm 404$ &  $4.1 \pm 0.14$ &  $3.0^{+0.21}_{-0.19}$ &     $172^{+40}_{-72}$ &       1 \\
    HIP 5626 &      A3V &    01:12:16.82 &   +79:40:26.27 &   5.600 &     12.07 &   $10342 \pm 352$ &  $4.2 \pm 0.14$ &  $2.4^{+0.15}_{-0.14}$ &   $218^{+102}_{-127}$ &       1 \\
    HIP 7345 &      A1V &    01:34:37.78 &   -15:40:34.90 &   5.619 &     16.84 &   $10007 \pm 340$ &  $4.4 \pm 0.14$ &  $2.2^{+0.12}_{-0.11}$ &   $156^{+130}_{-100}$ &       1 \\
    HIP 8016 &      B9V &    01:42:55.86 &   +70:37:21.09 &   5.177 &     11.75 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.21}$ &     $67^{+188}_{-57}$ &       2 \\
    HIP 8704 &    B1.5V &    01:51:59.32 &   +55:08:50.58 &   5.520 &      2.52 &  $22000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.8^{+0.74}_{-0.70}$ &         $8^{+6}_{-3}$ &       2 \\
      HR 545 &      B9V &    01:53:31.77 &   +19:17:46.27 &   4.700 &   \nodata &   $10000 \pm 500$ &  $4.5 \pm 0.25$ &  $2.2^{+0.21}_{-0.20}$ &     $34^{+106}_{-27}$ &       2 \\
    HIP 9312 &     A0Vn &    01:59:38.04 &   +64:37:17.76 &   5.283 &     13.28 &   $11913 \pm 405$ &  $4.1 \pm 0.14$ &  $2.8^{+0.13}_{-0.11}$ &      $77^{+65}_{-50}$ &       1 \\
    HIP 9564 &     A1Vn &    02:02:52.48 &   +64:54:05.27 &   5.999 &     11.92 &   $11266 \pm 383$ &  $4.3 \pm 0.14$ &  $2.7^{+0.15}_{-0.12}$ &     $149^{+74}_{-88}$ &       1 \\
      HR 604 &      B8V &    02:03:54.72 &   +42:19:51.41 &   5.820 &   \nodata &   $10000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.8^{+0.46}_{-0.42}$ &    $281^{+82}_{-117}$ &       2 \\
   HIP 10320 &      B9V &    02:12:54.47 &   -30:43:25.77 &   5.261 &     10.18 &   $11745 \pm 399$ &  $3.7 \pm 0.14$ &  $3.1^{+0.23}_{-0.19}$ &     $205^{+22}_{-43}$ &       1 \\
   HIP 10670 &    A1Vnn &    02:17:18.87 &   +33:50:49.90 &   4.000 &     29.04 &   $10772 \pm 366$ &  $4.2 \pm 0.14$ &  $2.6^{+0.16}_{-0.13}$ &    $230^{+63}_{-109}$ &       1 \\
   HIP 10732 &     A1Vn &    02:18:07.54 &   +19:54:04.19 &   5.575 &      7.29 &   $9500 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.1^{+0.37}_{-0.31}$ &    $107^{+286}_{-93}$ &       2 \\
   HIP 11345 &      A0V &    02:25:57.01 &   -12:17:25.71 &   4.869 &      7.15 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.25}_{-0.22}$ &     $72^{+206}_{-60}$ &       2 \\
   HIP 12332 &      A7V &    02:38:48.99 &   +21:57:41.06 &   5.454 &      9.68 &    $8000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.0^{+0.40}_{-0.33}$ &   $621^{+269}_{-268}$ &       2 \\
   HIP 12706 &     A2Vn &    02:43:18.04 &   +03:14:08.94 &   3.470 &     40.97 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.13}$ &   $647^{+104}_{-184}$ &       1 \\
   HIP 12719 &      B3V &    02:43:27.11 &   +27:42:25.72 &   4.670 &      9.51 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.62}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
   HIP 12803 &     B9Vn &    02:44:32.97 &   +15:18:42.71 &   5.776 &      5.49 &  $12000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.8^{+0.39}_{-0.36}$ &      $25^{+63}_{-17}$ &       2 \\
   HIP 13165 &      B6V &    02:49:17.56 &   +17:27:51.52 &   5.314 &      4.18 &  $16000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.4^{+0.55}_{-0.51}$ &       $13^{+22}_{-7}$ &       2 \\
   HIP 13202 &      A0V &    02:49:54.18 &   -27:56:31.14 &   5.389 &      7.11 &    $9000 \pm 500$ &  $3.5 \pm 0.25$ &  $2.4^{+0.44}_{-0.38}$ &   $401^{+138}_{-170}$ &       2 \\
   HIP 13209 &     B8Vn &    02:49:59.03 &   +27:15:37.83 &   3.606 &     19.69 &   $13316 \pm 453$ &  $4.1 \pm 0.14$ &  $3.3^{+0.15}_{-0.13}$ &      $45^{+43}_{-30}$ &       1 \\
   HIP 13327 &      B7V &    02:51:29.59 &   +15:04:55.45 &   5.514 &      6.60 &  $14000 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.8^{+0.55}_{-0.46}$ &      $36^{+57}_{-27}$ &       2 \\
   HIP 13717 &      A3V &    02:56:37.42 &   -03:42:44.35 &   5.160 &     17.49 &    $8612 \pm 293$ &  $4.0 \pm 0.14$ &  $1.9^{+0.13}_{-0.11}$ &   $571^{+138}_{-255}$ &       1 \\
   HIP 13879 &     A2Vn &    02:58:45.67 &   +39:39:45.81 &   4.700 &     10.53 &    $9298 \pm 316$ &  $3.5 \pm 0.14$ &  $2.1^{+0.12}_{-0.09}$ &   $340^{+141}_{-193}$ &       1 \\
   HIP 14043 &      B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.48}_{-0.45}$ &      $17^{+33}_{-10}$ &       2 \\
   HIP 14143 &      B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &  $14000 \pm 1000$ &  $4.5 \pm 0.25$ &  $3.6^{+0.50}_{-0.45}$ &      $17^{+36}_{-11}$ &       2 \\
   HIP 14293 &      A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &    $8039 \pm 273$ &  $4.2 \pm 0.14$ &  $1.8^{+0.14}_{-0.10}$ &   $782^{+166}_{-291}$ &       1 \\
   HIP 14576 &      B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.29}_{-0.24}$ &     $139^{+16}_{-25}$ &       1 \\
   HIP 14764 &      B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.47}_{-0.40}$ &     $54^{+103}_{-44}$ &       2 \\
   HIP 14862 &    A2Vnn &    03:11:56.27 &   +74:23:37.17 &   4.840 &     19.72 &   $8875 \pm 1000$ &  $4.2 \pm 0.25$ &  $1.8^{+0.32}_{-0.29}$ &     $71^{+317}_{-60}$ &       2 \\
   HIP 15110 &      A1V &    03:14:54.10 &   +21:02:40.01 &   4.880 &     12.44 &    $9902 \pm 337$ &  $4.0 \pm 0.14$ &  $2.4^{+0.18}_{-0.15}$ &    $375^{+52}_{-104}$ &       1 \\
   HIP 15338 &      B8V &    03:17:47.35 &   +44:01:30.08 &   5.478 &      4.46 &  $12000 \pm 1000$ &  $3.5 \pm 0.25$ &  $3.5^{+0.65}_{-0.59}$ &     $155^{+68}_{-59}$ &       2 \\
   HIP 15404 &      B3V &    03:18:37.74 &   +50:13:19.83 &   5.158 &      5.12 &  $20000 \pm 1000$ &  $4.5 \pm 0.25$ &  $6.5^{+0.68}_{-0.64}$ &         $9^{+9}_{-4}$ &       2 \\
   HIP 15444 &      B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.5^{+0.60}_{-0.60}$ &       $11^{+14}_{-6}$ &       2 \\
   HIP 16147 &      B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.59}_{-0.58}$ &       $11^{+14}_{-5}$ &       2 \\

@@

   HIP 16244 &      B3V &    03:29:22.05 &   +49:30:32.21 &   4.678 &      6.05 &  $18000 \pm 1000$ &  $4.5 \pm 0.25$ &  $5.4^{+0.61}_{-0.57}$ &       $11^{+14}_{-5}$ &       2 \\
   HIP 16285 &      A5V &    03:29:55.15 &   -42:38:03.32 &   5.768 &     15.28 &    $7884 \pm 268$ &  $3.9 \pm 0.14$ &  $1.7^{+0.13}_{-0.09}$ &   $841^{+183}_{-335}$ &       1 \\
   HIP 16322 &     A0Vn &    03:30:24.47 &   +11:20:11.19 &   5.125 &      9.03 &   $10000 \pm 500$ &  $4.0 \pm 0.25$ &  $2.3^{+0.26}_{-0.22}$ &     $80^{+200}_{-69}$ &       2 \\
   HIP 16340 &      B8V &    03:30:36.95 &   +48:06:12.95 &   5.820 &      3.65 &  $12000 \pm 1000$ &  $4.0 \pm 0.25$ &  $2.9^{+0.48}_{-0.40}$ &     $54^{+107}_{-44}$ &       2 \\
